Concurrent Programming with CXL

### 2020-06-17 book/paper.tex
Latest

\section*{CXL Values}

@@

@@

The \texttt{Frame} instruction has three arguments: the name of the method,
a list containing the names of the arguments of the method, and
the program counter of the method's \texttt{Return} instruction.
The code generated from \texttt{count := count + 1} in line 2 of
\texttt{Up.cxl} is as follows:

@@

Mutual exclusion is an example of a \emph{safety property},
\index{safety property}
a property that ensures that \emph{nothing bad will happen}, in this case
two processes being in the critical section.
What we need now a \emph{liveness property}:
\index{liveness property}
we want to ensure that
\emph{eventually something good will happen}.
There are various possible liveness properties we could use,
but here we will propose the following informally: if some set of processes
$S$ are trying to enter the critical section and any process already in the
intersection eventually leaves, then eventually one process in $S$ will enter
the critical section.
We call this \emph{progress}.
\index{progress}

@@

\begin{quote}
Try it out!
\begin{itemize}
\item Plug \texttt{while True: pass;;} for entering the critical section
in Figure~\ref{fig:cs} and run CXL.  It should print a trace
to a state from which a terminating state cannot be reached.
\end{itemize}
\end{quote}

@@

@@

\chapter{List of Machine Instructions}

@@

\printindex

\printglossaries

>>>>

\section*{CXL Values}
\label{ap:cxlvalues}

@@

Appendix~\ref{ap:cxlvalues} provides details on all the values that
CXL currently supports.

@@

Appendix~\ref{ap:cxlbytecode} provides a list of all CVM machine instructions,
in case you want to read about the details.
The \texttt{Frame} instruction has three arguments: the name of the method,
a list containing the names of the arguments of the method, and
the program counter of the method's \texttt{Return} instruction.
The code generated from \texttt{count := count + 1} in line 2 of
\texttt{Up.cxl} is as follows:

@@

Mutual exclusion is an example of a \emph{safety property},
\index{safety property}
a property that ensures that \emph{nothing bad will happen}, in this case
two processes being in the critical section.
What we need now a \emph{liveness property}:
\index{liveness property}
we want to ensure that
\emph{eventually something good will happen}.
There are various possible liveness properties we could use,
but here we will propose the following informally: if there exists a non-empty
set $S$ of processes that are trying to enter the critical section and any
process already in the intersection eventually leaves, then eventually one
process in $S$ will enter the critical section.
We call this \emph{progress}.
\index{progress}

@@

@@

\section*{Exercises}
\begin{enumerate}
\item Run Figure~\ref{fig:cs} using CXL.  As there is no protection of the critical
section, mutual is violated, the assertion should fail, and a trace should be reported.
Now plug \texttt{while True: pass;;} before entering the critical section
in Figure~\ref{fig:cs} and run CXL again.  Now mutual exclusion is guaranteed but
progress is violated.  CXL should print a trace
to a state from which a terminating state cannot be reached.
Describe in English the difference in the failure reports.
\item If we change the loop in Figure~\ref{fig:cs} into an infinite loop,
does the \emph{progress} property guarantee that all processes that are trying
to enter eventually enter?  Why or why not?
\end{enumerate}

@@

\chapter{List of Machine Instructions}
\label{ap:cxlbytecode}

@@

\newpage
\printindex

\newpage
\printglossaries
